---
title: "STAT 547M Homework 6"
author: "Tian Gao"
date: "Oct 29, 2018"
output:
  html_document:
    keep_md: true
    toc: true
    toc_depth: 2
    theme: readable
---
# Bring rectangular data in
```{r}
## load gapminder
suppressPackageStartupMessages(library(gapminder))
## load tidyverse
suppressPackageStartupMessages(library(tidyverse))
## load testthat
suppressPackageStartupMessages(library(testthat))
## load stringi
suppressPackageStartupMessages(library(stringi))
## load leaflet
suppressPackageStartupMessages(library(leaflet))
```



# Install and load `ggmap` package

```{r}
#install ggmap
#install.packages("devtools")
#devtools::install_github("dkahle/ggmap", ref = "tidyup")
#load ggmap
suppressPackageStartupMessages(library(ggmap))
#register API key (please do not use this key for any other purpose, thank you)
#register_google(key = "AIzaSyBsFRsHrAmuPDmcWd-7D5AbENG6_XreKDo")
```

# Task 1: Character data
## Exercise 14.2.5

(1)In code that doesn¡¯t use stringr, you¡¯ll often see paste() and paste0(). What¡¯s the difference between the two functions? What stringr function are they equivalent to? How do the functions differ in their handling of NA?

* Solution: The difference is that 'paste()' allows us to add separator when we want to concatenate strings, while 'paste0()' can not. 'paste()' and 'paste0()' are equivalent to 'str_c()'.  For 'paste()' and 'paste0()', NA is directly converted to string 'NA'. If NA is one of the input string of 'str_c()', the output of str_c() will become NA. The following are some example:
```{r}
str_c("hello", "world")
str_c("hello", "world", sep=" ")
paste("hello", NA, sep=" ")
paste0("hello", NA)
str_c("hello", NA)
```


(2)In your own words, describe the difference between the sep and collapse arguments to str_c().

* Solution: If we use multiple strings as input, the strings will be concatenated with seperator put between neighbors. Collapse is used with vectors, collapse will be placed between the elements of same index. The following example will make this clear.

```{r}
a <- c("hello", "world")
b <- c("male", "female")
# seprator will be put between two strings
str_c("hello", "world", sep=" ")
# : is put between elements with same index
str_c(a,b,sep=":")
# seperator is put between two elements with same index to get a new vector and collapse is put between the element of the new vector
str_c(a,b,sep=">", collapse=",")
```

(3)Use str_length() and str_sub() to extract the middle character from a string. What will you do if the string has an even number of characters?

* Solution: 
```{r}
# if the length is odd
a <- 'hello'

str_sub(a,str_length(a)/2+1, str_length(a)/2+1 )

```
```{r}
# if the length is even
a <- "helloworld"
str_sub(a, str_length(a)/2, str_length(a)/2+1)
```

(4)What does str_wrap() do? When might you want to use it?

* Solution: 'str_wrap()' is used to seperate paragraph into several lines.  Following is an example. 

```{r}
string <- "Complicated problem broken down into sub-problems that are individually much simpler. Code is efficient, correct, and minimal. Code uses appropriate data structure (list, data frame, vector/matrix/array). Code checks for common errors"
cat(string)
cat(str_wrap(string))
```

(5)What does str_trim() do? What¡¯s the opposite of str_trim()?

* Solution: str_trim() delete all the heading and tailing spaces including Tab. The opposite of "str_trim()" is "str_pad()"
```{r}
with_space ="\thello world"
cat(str_trim(with_space))

without_space = "hello world"
str_pad(without_space, width=str_length(without_space)+8,
        side=c("left"),
        pad=" ")
```

(6)Write a function that turns (e.g.) a vector c("a", "b", "c") into the string a, b, and c. Think carefully about what it should do if given a vector of length 0, 1, or 2.

```{r}
tostring = function(v){
  if(length(v)==0){return("")}
  if(length(v)==1){return(v)}
  first=str_c(v[-length(v)], collapse = ", ")
  return(str_c(first, v[length(v)], sep = ", and "))
}
tostring(c())
tostring(c("a"))
tostring(c("a","b"))
tostring(c("a","b","c"))
```

## 14.3.1.1 Exercises

(1)Explain why each of these strings don¡¯t match a \: "\", "\\", "\\\".How would you match the sequence "'\?

* Solution: '\' is an escape character and is only meaningful when followed by some other character. '\\' is treated as '\' in R however is treated as escape character in regex, Thus it is also meaningless in regex. '\\\' will be interpreted as a back slash and and escape character in R, thus it is also illegal in regex. To match a '\', we can do the following:
```{r}
str_view('hello\\world', pattern="\\\\", match=TRUE)
```

* To match "'\ we can do the following:
```{r}
str_view("hello'\\world", pattern="\\'\\\\", match=TRUE)
```

(2)What patterns will the regular expression \..\..\.. match? How would you represent it as a string?

* Solution: Regex "\..\..\.." can match a string like ".a.b.c" whhere a,b,c can be any other character. Here is a example:
```{r}
str_view("hello.w.o.rld", pattern="\\..\\..\\..", match=TRUE)
```

## 14.3.2.1 Exercises

(1)How would you match the literal string "$^$"?
* The example is given below
```{r}
str_view("hello$^$world", pattern="\\$\\^\\$", match = TRUE)
```


(2)Given the corpus of common words in stringr::words, create regular expressions that find all words that:

* Start with ¡°y¡±.
```{r}
str_view(stringr::words, pattern="^y", match=TRUE)
```

* End with ¡°x¡±.
```{r}
str_view(stringr::words, pattern = "x$", match = TRUE)
```

* Are exactly three letters long. (Don¡¯t cheat by using str_length()!)
```{r}
str_view(stringr::words, pattern="^.{3}$",match=TRUE)
```

Have seven letters or more.
Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.
* Solutoin:
```{r}
str_view(stringr::words, pattern="^.{7,}$", match=TRUE)
```

##14.3.3.1 Exercises

(1)Create regular expressions to find all words that:

Start with a vowel.
* Solution:
```{r}
str_view(stringr::words, pattern="^[aeiou]", match=TRUE)
```
That only contain consonants. (Hint: thinking about matching ¡°not¡±-vowels.)

* Solution:
```{r}
str_view(stringr::words, pattern="[aeiou]", match=FALSE)
```
End with ed, but not with eed.
* Solution:
```{r}
str_view(stringr::words, pattern="[^e]ed$", match=TRUE)
```
End with ing or ise.

* Solution:
```{r}
str_view(stringr::words, pattern="ing$|ise$", match=TRUE)
```


(2)Empirically verify the rule ¡°i before e except after c¡±.
* Solution:
```{r}
str_subset(stringr::words, pattern = "[^c]ie")
```
* From the result we know that the i before e except after c is true.

Is ¡°q¡± always followed by a ¡°u¡±?

* Solution:
```{r}
str_view(stringr::words, pattern="q[^u]",match=TRUE)
```

* we can see that the result is empty, thus this statement is true. 


(3)Write a regular expression that matches a word if it¡¯s probably written in British English, not American English.

* In American English, "u"  between "o" and "r" is sometimes omitted. We can use this to detect British English
```{r}
str_view(c("favourite", "favorite", "honor", "honour", "color","colour"), pattern=".our", match=TRUE)
```

(4)Create a regular expression that will match telephone numbers as commonly written in your country.

* Solution: In Canada, the telephone number is in this format: +1 (xxx) xxx xxxx, we can build a regex based on this. 
```{r}
str_view(c("+1 (778) 522 0667", "+86 1836230399", "+123456789"), pattern="\\+1 \\([1-9]{3}\\) [0-9]{3} [0-9]{4}")
```

## 14.3.4.1 Exercises
(1)Describe the equivalents of ?, +, * in {m,n} form.

* Solution: ? is equivalent to {0,1}; + is equivilent to {1,}; * is equivalent to {0,}

(2)Describe in words what these regular expressions match: (read carefully to see if I¡¯m using a regular expression or a string that defines a regular expression.)

^.*$

* Solution: matches any string

"\\{.+\\}"

* Solution: matched at least one any character surrounded by {}

\d{4}-\d{2}-\d{2}

* Solution: matches a consecutive 4 digit followed by - followed by consecutive 2 digits followed by - followed by 2 consecutive digits, eg, 2018-11-11

"\\\\{4}"

* Solution: matches '\\\\'

(3)Create regular expressions to find all words that:

Start with three consonants.

* Solution:
```{r}
str_view(stringr::words, pattern="^[^aeiou]{3,}", match = TRUE)
```

Have three or more vowels in a row.

* Solution:
```{r}
str_view(stringr::words, pattern = "[aeiou]{3,}", match=TRUE)
```


Have two or more vowel-consonant pairs in a row.

* Solution:
```{r}
str_view(stringr::words, pattern="([aeiou][^aeiou]){2,}", match=TRUE)
```



Solve the beginner regexp crosswords at https://regexcrossword.com/challenges/beginner.

##14.3.5.1 Exercises
(1)Describe, in words, what these expressions will match:

(.)\1\1

* Solution: matches any acharacter that appears three times

"(.)(.)\\2\\1"

* Solution: matches two characters that appear in reversed order, eg, 'abba'

(..)\1

* Solution: matches two characters that repeats two times, eg, "abab"

"(.).\\1.\\1"

* Soltion: matched a string with 5 characters, first third and fifth are the same, the second and forth are any character, eg, "azaba"

"(.)(.)(.).*\\3\\2\\1"

* Solution: matches a string that the first three characters appear in reversed order at the string end, eg, "abcfjlksajfeioacba"

(2)Construct regular expressions to match words that:

Start and end with the same character.

* Solution:

```{r}
str_view(stringr::words, pattern = "^(.).*\\1$", match=TRUE)
```


Contain a repeated pair of letters (e.g. ¡°church¡± contains ¡°ch¡± repeated twice.)

* Solution:
```{r}
str_view(stringr::words, pattern = "(..).*\\1", match=TRUE)
```

Contain one letter repeated in at least three places (e.g. ¡°eleven¡± contains three ¡°e¡±s.)

* Solution:
```{r}
str_view(stringr::words, pattern=".*(.).*\\1.*\\1", match=TRUE)
```

## 14.4.2 Exercises
(1)For each of the following challenges, try solving it by using both a single regular expression, and a combination of multiple str_detect() calls.

Find all words that start or end with x.

* Solution:
```{r}
# regex
str_subset(stringr::words, pattern = "^x|x$")
#multiple str_detect()
a = str_detect(stringr::words, pattern = "^x")
b = str_detect(stringr::words, pattern = "x$")
stringr::words %>%
  `[`(a|b)
```

Find all words that start with a vowel and end with a consonant.

* Solution:
```{r}
# regex
str_subset(stringr::words, pattern = "^[aeiou].*[^aeiou]$")
#multiple str_detect()
a = str_detect(stringr::words, pattern="^[aeiou]")
b = str_detect(stringr::words, pattern="[^aeiou]$")
stringr::words %>%
  `[`(a & b)
```


Are there any words that contain at least one of each different vowel?

* Solution: for this one I need to write a function. From the code below we can see that there is no such words
```{r}
check <- function(string){
  unused = c("a", "e", "i", "o", "u")
  logic=as.logical(seq(from=1, to=1, along.with=string))
  for(i in unused){
    logic = logic & str_detect(string, pattern = i)
  }
  return(string[logic]);
}
for(i in (stringr::words)){
  check(i)
}
```







(2)What word has the highest number of vowels? What word has the highest proportion of vowels? (Hint: what is the denominator?)

* Solution:
```{r}
# highest number of vowels
counts = str_count(stringr::words, pattern = "[aeiou]")
stringr::words %>%
  '['(which(counts == max(counts)))

# highest proportion of vowels
counts = str_count(stringr::words, pattern = "[aeiou]")/str_length(stringr::words)
stringr::words %>%
  '['(which(counts == max(counts)))
```



##14.4.3.1 Exercises
(1)In the previous example, you might have noticed that the regular expression matched ¡°flickered¡±, which is not a colour. Modify the regex to fix the problem.

* To fix this problem, we need \b in regex. Here is the code:
```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match <- str_c(colours, collapse = "|")

# turn color vector into a regex
colour_match <- str_c("\\b", colour_match, "\\b")

more <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more, colour_match)
```
(2)From the Harvard sentences data, extract:

The first word from each sentence.

* Solution:
```{r}
str_extract(sentences, pattern="[a-zA-Z]+")
```

All words ending in ing.

* Solution:
```{r}
ing_words = str_extract_all(sentences, pattern = "\\b[a-zA-Z]+ing\\b", simplify = TRUE)
ing_words[ing_words!=""]
```

All plurals.

* Solution:
```{r}
a =  str_extract_all(sentences, pattern = '[a-zA-Z]+s', simplify = TRUE)
a[a!=""]
```

##14.4.4.1 Exercises
(1)Find all words that come after a ¡°number¡± like ¡°one¡±, ¡°two¡±, ¡°three¡± etc. Pull out both the number and the word.

* Solution:
```{r}
# define numbers
nums = c("zero","one","two","three","four","five","six","seven","eight","nine",
         "ten","eleven","twelve","thirteen","fourteen","fifteen","sixteen","seventeen","eighteen","nineteen",
         "twenty","thirty","forty","fifty","sixty","seventy","eighty","ninety",
         "hundred","thousand","million","billion","trillion")

# define pattern
pattern <- str_c("(", str_c(nums, collapse = "|"), ") ([^ \\.]+)")

a = str_extract_all(sentences, pattern = pattern, simplify = TRUE)
# exclude the empty ones
a[a!=""]
```

(2)Find all contractions. Separate out the pieces before and after the apostrophe.

* Solution:
```{r}
# patterns
pattern <- "([A-Za-z]+)'([A-Za-z]+)"
# get the contractions
contractions <- str_extract_all(sentences, pattern = pattern, simplify = TRUE)
# filter the empty ones
contractions = contractions[contractions!=""]
contractions
str_split(contractions, pattern = "'", simplify = TRUE)

```

##14.4.5.1 Exercises
(1)Replace all forward slashes in a string with backslashes.

* Solution:
```{r}
str_replace_all("hello///world", pattern = "/", "\\\\")
```

(2)Implement a simple version of str_to_lower() using replace_all().

* Solution:
```{r}
str_replace_all("HELLOWORLD", c("A"="a", "B"="b", "C"="c", "D"="d", "E"="e", "F"="f", "G"="g", "H"="h", "I"="i", "J"="j", "K"="k", "L"="l", "M"="m", "N"="n", "O"="o", "P"="p", "Q"="q", "R"="r", "S"="s", "T"="t", "U"="u", "V"="v", "W"="w", "X"="x", "Y"="y", "Z"="z"))
```

(3)Switch the first and last letters in words. Which of those strings are still words?

* Solution:
```{r}
# change the order of the characters

switch <- str_replace(stringr::words, pattern = "(^[a-zA-Z])([a-zA-Z]*)([a-zA-Z]$)", replacement = "\\3\\2\\1")

# find the ones that are still words
intersect(stringr::words, switch)
```


##Exercises 14.4.6.1

(1)Split up a string like "apples, pears, and bananas" into individual components.

* Solution:
```{r}
s = c("apples, pears, and bananas")
str_split(s, boundary("word"))[[1]]
```
(2)Why is it better to split up by boundary("word") than " "?

* Solution: Because there punctuations that is not whitespace

(3)What does splitting with an empty string ("") do? Experiment, and then read the documentation.

* Solution: string "" will split the string into single characters
```{r}
str_split(s,"")[[1]]
```

##14.5.1 Exercises
(1)How would you find all strings containing \ with regex() vs. with fixed()?

* Solution:
```{r}
str_subset(c("hello\\world","hello"), "\\\\")
str_subset(c("hello\\world", "hello"), fixed("\\"))
```
(2)What are the five most common words in sentences?

* Solution
```{r}
str_extract_all(sentences, boundary("word")) %>%
  unlist() %>%
  str_to_lower() %>%
  tibble() %>%
  set_names("words") %>%
  group_by(words) %>%
  count(sort = TRUE) %>%
  head(5)
```

##14.7.1 Exercises
(1)Find the stringi functions that:

Count the number of words.

* Solution:
```{r}
stringi::stri_count_words("hello world")
```

Find duplicated strings.

* Solution:

```{r}
stringi::stri_duplicated_any(c("hello", "hello", "world"))
```

Generate random text.

* Solution:

```{r}
stringi::stri_rand_strings(5,2)
```

(2)How do you control the language that stri_sort() uses for sorting?

* Solution: we can use language argument in stri_sort function for example, stri_sort(french_words, french = TRUE)