---
title: "STAT 547M Homework 6"
author: "Junbin ZHANG"
date: "Oct 30, 2018"
output:
  html_document:
    keep_md: true
    toc: true
    toc_depth: 2
    theme: readable
---

# Bring rectangular data in
```{r}
## load gapminder
suppressPackageStartupMessages(library(gapminder))
## load tidyverse
suppressPackageStartupMessages(library(tidyverse))
## load testthat
suppressPackageStartupMessages(library(testthat))
## load stringi
suppressPackageStartupMessages(library(stringi))
## load leaflet
suppressPackageStartupMessages(library(leaflet))
```

# Install and load `singer` package

```{r}
## install singer
# install.packages("devtools")
#devtools::install_github("JoeyBernhardt/singer")
## load singer
suppressPackageStartupMessages(library(singer))
```

# Install and load `ggmap` package

```{r}
## install ggmap
# install.packages("devtools")
# devtools::install_github("dkahle/ggmap", ref = "tidyup")
## load ggmap
suppressPackageStartupMessages(library(ggmap))
## register API key (please do not use this key for any other purpose, thank you)
register_google(key = "AIzaSyDJnU2gOUgrDiIOSdujwanq9yX2yqRVlu4")
```

## Work with the`singer`data
Let's first have a preview of `single_locations` dataframe, in order to know why it is "dirty".
```{r}
# show previews of single_locations
head(singer_locations) %>% 
  # select columns we care about
  select(track_id, latitude, longitude, name, city) %>% 
  knitr::kable(col.names = c("Track ID", "Latitude", "Longitude", "Name", "City"))
tail(singer_locations) %>% 
  # select columns we care about
  select(track_id, latitude, longitude, name, city) %>% 
  knitr::kable(col.names = c("Track ID", "Latitude", "Longitude", "Name", "City"))
```

So the dataframe is "dirty" because it contains `NA` values. Therefore, the first thing we need to do is to filter out rows with `NA` latitude or longitude.

```{r}
# filter out latitude and longitude with NA
singer_locations_no_na <- singer_locations %>% 
  filter(!is.na(latitude) | !is.na(longitude))
# show previews of filtered dataframe
head(singer_locations_no_na) %>% 
  # select columns we care about
  select(track_id, latitude, longitude, name, city) %>% 
  knitr::kable(col.names = c("Track ID", "Latitude", "Longitude", "Name", "City"))
tail(singer_locations_no_na) %>% 
  # select columns we care about
  select(track_id, latitude, longitude, name, city) %>% 
  knitr::kable(col.names = c("Track ID", "Latitude", "Longitude", "Name", "City"))
```

In the next step, we use `map2()` (since we need to input both latitude and longitude) of `purrr` and `revgeocode()` of `ggmap` to get the cities. Her we use `revgeocode()` as a **formula** instead of a **function** inside `map2()`. According to [this reference](https://www.rdocumentation.org/packages/purrr/versions/0.2.5/topics/map2), we need to add "~" before the function name, and use ".x" and ".y" to represent those two arguments.

In addtion, since there are more than 4,000 rows in `singer_locations_no_na`, and it requires billing on Google Clouds Services, we only use the first 30 rows as an example. However, this solution can be easily extended to handle the whole dataframe.

```{r, message = FALSE}
# trim singer_locations_no_na for the top 100 rows
trim_locations <- singer_locations_no_na %>% 
  slice(1:20)
# use ggmap to get locations
ggmap_locations <- map2_chr(trim_locations$longitude, trim_locations$latitude, ~ revgeocode(as.numeric(c(.x, .y))))
```

Here we apply `map2_chr()` to make the results as a vector of strings instead of a list to get rid of unnecessary information.

```{r}
# show the final results
cbind(trim_locations$city, ggmap_locations) %>% 
  knitr::kable(col.names = c("City in `singer_locations`", "City Obtained by `ggmap`"))
```

## Task 2.2

**Try to check wether the place in `city` corresponds to the information you retrieved.**

Having a closer look at the above table, there is another point that make `city` dirty: the way to name a city are not the same accoss the column, for example, "UK - England - London" is a weired expression.

However, we can perform some preprocessing on the data to finish this task:

- We first extract words from every string, and convert them into lower case for further processing.
- Based on some knowledge on the states of America, we replace all full state names into their abbreviations.

In the end, we try to find the intersection of the original `city` and the ones obtained from `ggmap`. If there is at least one match for a row, then we get the right result.

```{r}
# create pattern for replacement
patterns <- c("new york" = "ny", "pennsylvania" = "pa", "california" = "ca", "washington" = "wa", "louisiana" = "la")
## preprocessing
ori_words <- trim_locations$city %>%
  # convert to lower case
  str_to_lower() %>% 
  # split into words
  str_split(pattern = boundary("word")) %>%
  # replace state names
  map(str_replace_all, patterns)
ggmap_words <- ggmap_locations %>% 
  # convert to lower case
  str_to_lower() %>% 
  # split into words
  str_split(pattern = boundary("word")) %>%
  # replace state names
  map(str_replace_all, patterns)
## find intersection and check if there are at least one match
correct <- map2(ori_words, ggmap_words, ~intersect(.x, .y)) %>% 
  map(function(l) {
    return(length(l) >= 1)
  })
# show results
cbind(trim_locations$city, ggmap_locations, correct) %>% 
  knitr::kable(col.names = c("City in `singer_locations`", "City Obtained by `ggmap`", "Correct?"))
```

So there is only one incorrect result at line 15.

```{r}
# print incorrect results
cbind(trim_locations$city, ggmap_locations, correct) %>% 
  # convert to tibble
  as_tibble() %>% 
  # filter to have incorrect results
  filter(correct == FALSE) %>% 
  # select out column correct
  select(-correct) %>% 
  # show table
  knitr::kable(caption = "Incorrect Result", col.names = c("City in `singer_locations`", "City Obtained by `ggmap`"))
```


## Task 2.3

**If you still have time, you can go visual.**

```{r}
# use leaflet to plot information
singer_locations_no_na %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircles(
    lat = singer_locations_no_na$latitude,
    lng = singer_locations_no_na$longitude,
    # here the popup contains city, title, artist name and year
    popup = str_c(singer_locations_no_na$city, ": ", singer_locations_no_na$title, " by ", singer_locations_no_na$artist_name, " in ", singer_locations_no_na$year)
  ) %>% 
  addProviderTiles(providers$OpenStreetMap)
```
    